Mg Depleted and K Enriched Stars from LAMOST Spectral Data

### 2018-01-10 article/ms.tex
changes to abstract, method and intro. Not yet added sections describing methodology of Kevin's observations, or todays filter to 23 stars

% Abstract of the paper
\begin{abstract}

\end{abstract}

@@

A spectroscopic study of RGB giant stars in NGC 2419 led to the discovery discovery of a strong anti-correlation between Mg and K in around 30-40 \% of the studied stars, along with weaker relations in Si, Sc, Ca, Ti and V (\citet{mucciarelli2012}, \citet{cohenkirby2012}). Depletions of Mg within globular clusters are not uncommon, but they are always accompanied with an increase in [Fe/H]. The mechanism for this phenomena is the introduction of $\alpha$ poor but iron rich material released from Type Ia supernovae locally polluting the 'normal' [Mg/Fe] material released from Type II supernovae. However, the two sub-populations in NGC 2419 are indistinguishable in their [Fe/H] abundance \citep{cohenkirby2012}. Further, Type Ia supernovae enrichment does not account for the enhanced K abundance or trends in the other elements.

@@

With the exception of NGC 2808, in which all 4 of its known Mg depleted stars have been found to have an anti-correlation with K \citep{mucciarelli2015}, this signature has thus far been found to be contained within NGC 2419. A  targeted search looking [K/Fe] in RGB stars from clusters NGC 6752, NGC 6121, NGC 1904, and $\omega$ Centauri as well as 21 field stars found in all cases K abundances falling within the range of the Mg normal population in NGC 2419 \citep{carretta2013}.

@@

It has been suggested that the NGC 2419's position and size, being both very massive and very distant from the Milky Way compared to many other globular clusters, aids it in retaining enriched material from explosive events \citep{mucciarelli2012}. It is also perhaps noteworthy that NGC 2808 is also one of the more massive globular clusters of the Milky Way, although it is far closer to the Galactic Centre. But if this unknown pollution event is common among globular clusters and the cause of its apparent exclusivity to NGC 2808 and NGC 2419 is enhanced ejecta retention due to high mass, then other massive clusters such as $\omega$ Centauri would also be expected contain the signature, which to date has not been observed.

While it is plausible that the increased mass and greater distance from the gaseous disk of the Milky Way would cause a clusters first generation polluter stars to have an increased effect on the second generation of stars, this effect would apply to all ejecta (assuming comparable energies). So while it might be expected that second generation stars in clusters similar to NGC 2419 made up of more material processed by the first generation than other lighter globular clusters, it doesn't explain why the ejecta from the first generation was apparently dominated by this as yet unknown polluter object resulting in the Mg-K anti-correlation. In the opinion of the author, it is the identity and physical characterisation of this unknown polluter that is of the greatest scientific interest, with such a result also hopefully answering the question as to the signatures uniqueness.

An early modelling attempt at replicating the anomalous abundances in NGC 2419 assumed hot-bottom burning in AGB and super-AGB (SAGB) stars \citep{ventura2012}. This study succeeded in reproducing the Mg-K anti-correlation, using nuclear reaction pathway \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(e^-,\nu)^{37}Cl(p,\gamma)^{38}Ar(p,\gamma)^39K} (corrected as per \cite{iliadis2016}) for nuclear synthesis of K. However, the required abundance patterns consistent with NGC 2419 were only attainable if the reaction cross section was set to 100 times the commonly accepted rate or temperatures could be made higher than currently accepted values, achieving a burning temperature of 150 MK.

A more recent, comprehensive attempt to replicate the Mg and K abundances in NGC 2419 by \cite{iliadis2016} also attempted to reproduce the abundances of Si, Sc, Ca, Ti and V (elements reported as having weak correlations with Mg by \cite{cohenkirby2012}). The ultimate goal was to constrain the temperatures and densities required to produce the chemical signiature, and thereby provide insight into potential polluter candidates. It is perhaps noteworthy that they identified a diferent main reaction pathway to that of \cite{ventura2012}, which is relegated to a minor minor seccondary pathway. The main pathway they identify is \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(p,\gamma)^{38}K(\beta ^+ \nu)^{38}Ar(p,\gamma)^39K}.

@@

This study, which queries 454180 LAMOST giants for depleted Mg and enhanced K, seeks to provide additional information which can be used to guide and test models attempting to explain the Mg-K anti-correlation and related phenomena. The large sample size provides greater insight into the supposed exclusivity of the signature, and any stars identified present an important opportunity for follow up observations both to confirm the abundance signature and to determine data beyond the scope of this study such as the mass and orbital characteristics of the targets.

@@

The vetting process was done through visual examination of each case. The minimum criterion for a pass was two out of the three Mg lines to look at least plausibly depleted, and at least one of the K lines to look convincing. The apparent noisiness of the signal was qualitatively taken into account when making these determinations. Of the 384 candidates manually vetted, 188 were ultimately determined to be sufficiently strong to be reported. The 6556 \AA \\ H line was then visually examined for each star to identify stars with active chromosphere emissions which could result in false positives for Mg depletion. 62 stars were removed from the sample due to being chromospheric emmiters. A further 13 stars were removed due to the model fitted poorly to the H 6556 line possibly due to incorrect log(g) or $\text{T}_{\text{eff}}$ estimates from \textit{The Cannon}, leaving a total of 113 candidates displaying depleted Mg and enhanced K.

>>>>

% Abstract of the paper
\begin{abstract}
454180 RGB stars from the low resolution LAMOST DR2 survey were searched for anomalously high K and depleted Mg signatures. This study represents the largest search for field stars containing the Mg-K anti-correlation so far identified only in the globular NGC 2419 and NGC 2808. 23 stars displaying absorption spectra with over-abundant K and depleted Mg accross a range of metalicities were identified, but none were identified as having [Mg/Fe] or [K/Fe] consistent with the Mg depleted population found in NGC 2419. The abundances in these 23 stars are estimated at ranging between [INSERT RANGE FOR K AND MG HERE BASED OFF LAMOST DATA]. High resolution spectra for three stars (1 of which is not included among the final count of 23 spectral candidates for the signiature for reasons relating to the LAMOST signal quality for that star, despite having the highest K abundance of the three at [K/Fe]=1.54) selected based on observability characteristics were obtained using the Las Campanas Observatory, and for these stars elemental abundances for heavy elements such as Sc and V are also presented.
\end{abstract}

@@

A spectroscopic study of RGB giant stars in NGC 2419 led to the discovery discovery of a strong anti-correlation between Mg and K in around 30-40 \% of the studied stars, along with weaker relations in Si, Sc, Ca, Ti and V (\citet{mucciarelli2012}, \citet{cohenkirby2012}). Depletions of Mg within globular clusters are not uncommon, but are always accompanied with an increase in [Fe/H]. The mechanism for this phenomena is the introduction of $\alpha$ poor but iron rich material released from Type Ia supernovae locally polluting the 'normal' [Mg/Fe] material released from Type II supernovae. However, the two sub-populations in NGC 2419 are indistinguishable in their [Fe/H] abundance \citep{cohenkirby2012}. Further, Type Ia supernovae enrichment does not account for the enhanced K abundance or trends in the other elements.

@@

With the exception of NGC 2808, in which all 4 of its known Mg depleted stars have been found to have an anti-correlation with K \citep{mucciarelli2015}, this signature has thus far been found to be contained within NGC 2419. A  targeted search looking [K/Fe] in RGB stars from clusters NGC 6752, NGC 6121, NGC 1904, and $\omega$ Centauri as well as 21 field stars found in all cases K abundances falling within the bounds of the Mg normal population in NGC 2419 \citep{carretta2013}.

@@

It has been suggested that NGC 2419's position and size, being both very massive and very distant from the Milky Way compared to many other globular clusters, aids it in retaining enriched material from explosive events \citep{mucciarelli2012}. It is also perhaps noteworthy that NGC 2808 is also one of the more massive globular clusters of the Milky Way, although it is far closer to the Galactic Centre. But if this unknown pollution event is common among globular clusters and the cause of its apparent exclusivity to NGC 2808 and NGC 2419 is enhanced ejecta retention due to high mass, then other massive clusters such as $\omega$ Centauri would also be expected contain the signature, which to date has not been observed.

While it is plausible that the increased mass and greater distance from the gaseous disk of the Milky Way would cause a clusters first generation polluter stars to have an increased effect on the second generation of stars, this effect would apply to all ejecta (assuming comparable energies). So while it might be expected that second generation stars in clusters similar to NGC 2419 made up of more material processed by the first generation than other lighter globular clusters, it doesn't explain why the ejecta from the first generation was apparently dominated by this as yet unknown polluter object resulting in the Mg-K anti-correlation. In the opinion of the author, it is the identity and physical characterisation of this unknown polluter that is of the greatest scientific interest, with such a result also hopefully answering the question of the signatures uniqueness.

An early modelling attempt at replicating the anomalous abundances in NGC 2419 assumed hot-bottom burning in AGB and super-AGB (SAGB) stars \citep{ventura2012}. This study succeeded in reproducing the Mg-K anti-correlation, using the nuclear reaction pathway \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(e^-,\nu)^{37}Cl(p,\gamma)^{38}Ar(p,\gamma)^39K} (corrected as per \cite{iliadis2016}) for nuclear synthesis of K. However, abundance patterns consistent with NGC 2419 were only attainable if the reaction cross section was set to 100 times the commonly accepted rate or temperatures could be made higher than currently accepted values, achieving a burning temperature of 150 MK.

A more recent, comprehensive attempt to replicate the Mg and K abundances in NGC 2419 by \cite{iliadis2016} also attempted to reproduce the abundances of Si, Sc, Ca, Ti and V (elements reported as having weak correlations with Mg by \cite{cohenkirby2012}). The ultimate goal was to constrain the temperatures and densities required to produce the chemical signiature, and thereby provide insight into potential polluter candidates. It is perhaps noteworthy that they identified a diferent main reaction pathway for K nucleosynthesis to that of \cite{ventura2012}, which is relegated to a minor minor seccondary pathway. The main pathway they identify is \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(p,\gamma)^{38}K(\beta ^+ \nu)^{38}Ar(p,\gamma)^39K}.

@@

This study, which queries 454180 LAMOST giants for depleted Mg and enhanced K, seeks to provide additional information which can be used to guide and test models attempting to explain the Mg-K anti-correlation and related phenomena. The large sample size provides greater insight into the supposed exclusivity of the signature, and the stars identified present an important opportunity for follow up observations.

@@

The vetting process was done through visual examination of each case. The minimum criterion for a pass was two out of the three Mg lines to look at least plausibly depleted, and at least one of the K lines to look convincing. The apparent noisiness of the signal was qualitatively taken into account when making these determinations. Of the 384 candidates manually vetted, 188 were ultimately determined to be sufficiently strong for further examination based on the spectra around the K and Mg lines.

The 6556 \AA \\ H line was then visually examined for each star to identify stars with active chromosphere emissions which could result in false positives for Mg depletion. 62 stars were removed from the sample due to being chromospheric emmiters. A further 13 stars were removed due to the model fitted poorly to the H 6556 line possibly due to incorrect log(g) or $\text{T}_{\text{eff}}$ estimates from \textit{The Cannon}, leaving a total of 113 candidates displaying depleted Mg and enhanced K.
